Exploring and Validating the Motives Behind API Evolution: A Case Study

### 2015-03-20 rmtw/a6/latex8.tex
Merged sentence and re-added validity threats

\subsection{Data Collection}
The data were collected primarily through third degree methods, such as first hand inspections of the source code and the archival analysis of accompanying  documentation. The source code was comprised of two versions of APIs which the company had developed. An older version which is currently released and a newer version which is soon to be deployed. Each version of the API had its own respective documentation. The documentation was analysed to find explanations of the features offered by the API.

From the APIs we collected data about method names, parameters and return types. The data were collected from both versions of the APIs, with the changes between the two versions being of particular interest. From the archival documentation we collected information regarding the motive behind the functionality in API calls. The reason this was analysed was to provide insight into the motives behind the changes. For example, we examined differences in descriptions of methods prior to and after parameters were renamed.

To reduce risks of research bias and human error, the data collection was performed by both researchers individually and indepenedtly. If the data differed, the cause was investigated and resolved. As part of the collection phase, the data were input into tables and spreadsheets, according to the API version.

@@

>>>>

\subsection{Data Collection}
The data were collected primarily through third degree methods, such as first hand inspections of the source code and the archival analysis of accompanying  documentation. The source code was comprised of two versions of APIs which the company had developed. An older version which is currently released and a newer version which is soon to be deployed. Each version of the API had its own respective documentation. The documentation was inspected and organised to find explanations of the features offered by the API.

From the APIs we collected data about method names, parameters and return types. The data were collected from both versions of the APIs, with the changes between the two versions being of particular interest. The collected data were input into tables and spreadsheets, according to the API version. From the archival documentation we collected data regarding the motive behind the functionality in API calls. Data gathered from the documentation was also stored in tables and spreadsheets and was organised together with its corresponding method.

To reduce risks of research bias and human error, the data collection was performed by both researchers individually and independently. If the data differed, the cause was investigated and resolved.

@@

\subsection{Validity Threats}
This section highlights how we have either diminished or overcome the most concerning validity threats facing our study.

%Internal Validity
\textit{Internal Validity} threats for our study have been greatly reduced by the methodologies we have employed. By performing a individual inspection of  the API source code, documentation and individual results analysis, \textit{internal validity} is significantly reduced. Triangulation of the results with the use of interviewing the architects is key step in reducing potential validity threats in our study.

%External Validity
Regarding \textit{external validity}, generalisability and the appropriateness of our results are at risk. In our study we have striven to ensure that our findings will be as useful as possible to others. Given that there are some similar studies to ours and that ours is an exploratory study, our results will be useful to others who perform similar studies in the future. Our results come from both APIs either in production or soon to be in production. As such, the results of this study will hopefully be of use to the company at which they were studied, be it now for their current API or in the future when they inevitably develop others. Likewise, other companies in similar positions could use the results of our study when creating their own APIs.

%Reliability
The largest \textit{reliability} threat facing our study was the reproducibility. To counter this threat, we have provided a clear and concise coding method for the collected data. Furthermore, as mentioned previously, we have attempted to limit bias and ambiguity in our interview questions where possible. To ensure clarity of the questions, we have field tested the interview with some of our peers, altering the questions based on their feedback.

[!!!Note to Richard \#4: We struggled to find construct threats as we've not done the study so we don't know any yet, is it normal or OK to exclude one of the categories?]
